Equations & R Code

### 2016-06-03 manuscript/manuscript.Rmd
makes fig captions sans serif

---
layout: 12pt
header-includes:
   - \usepackage{lineno}
   - \linenumbers
bibliography: ~/Dropbox/Bibliography/CoexistStability.bib
csl: components/ecology.csl

>>>>

---
layout: 12pt
header-includes:
   - \usepackage{lineno}
   - \linenumbers
   - \usepackage[font={sf,small}]{caption}
bibliography: ~/Dropbox/Bibliography/CoexistStability.bib
csl: components/ecology.csl
